---
title: "Enrollment"
author: "Julius Gunnemann"
date: "2/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(readxl)
library(tidyverse)
library(janitor)
library(reprex)
library(gt)

```

```{r}
x <- read_excel("ces.xlsx", skip = 3) %>% 
  clean_names() %>%
  filter(! is.na(course_name)) %>%
  filter(course_department == "Government") %>%
  arrange(desc(total)) %>%
  slice(1:5) %>%
  select(course_title, course_name, instructor_full_name, total)  %>%
  gt() %>%
  tab_header(
    title = "Course Enrollment - Government",
    subtitle = glue::glue("Top five classes with highest enrollment")) 
  
```

```{r}
y %>%
  group_by(course_department) %>%
  summarize(total=sum(total)) %>%
  arrange(desc(total)) %>%
  
   
```  

  clean_names() %>%
  filter(! is.na(course_name)) %>%
  filter(course_department == "Government") %>%
  arrange(desc(total)) %>%
  slice(1:5) %>%
  select(course_title, course_name, instructor_full_name, total)  %>%
  gt() %>%
  tab_header(
    title = "Course Enrollment - Government",
    subtitle = glue::glue("Top five classes with highest enrollment")) 
  
```

  gt() %>%
  tab_header(
    title = "Course Enrollment - Government",
    subtitle = glue::glue("Top five classes with highest enrollment")
```

    
   group_by(course_department) %>%
  filter(course_department == "Government") 
  
arrange(desc(total)) %>%
  slice(1:5) %>%
  select(course_title, course_name, instructor_full_name, total) %>%

```

